
\begin{center}
    \footnotesize
    \renewcommand*{\arraystretch}{1.4}
    \begin{tabularx}{\textwidth}{c X}
        Book Chap.      & \underline{E. Fekhari}, B. Iooss, J. Muré, L. Pronzato and M. J. Rendas (2023). 
                        ``Model predictivity assessment: incremental test-set selection and accuracy evaluation''. 
                        In: \textit{Studies in Theoretical and Applied Statistics}, pages 315--347. Springer.\\
        \hline  
        Jour. Pap.      & \underline{E. Fekhari}, V. Chabridon, J. Muré and B. Iooss (2024).
                        ``Given-data probabilistic fatigue assessment for offshore wind turbines using Bayesian quadrature''. 
                        In: \textit{Data-Centric Engineering}, In press.\\

                        & E. Vanem, \underline{E. Fekhari}, N. Dimitrov, M. Kelly, A. Cousin and M. Guiton (2024).
                        ``A joint probability distribution for multivariate wind-wave conditions and discussions on uncertainties''.
                        In: \textit{Journal of Offshore Mechanics and Arctic Engineering}, In press.\\
        \hline
\shortstack{Int. Conf.\\Pap.} & \underline{E. Fekhari}, M. Baudin, V. Chabridon, and Y. Jebroun (2021). 
                                ``otbenchmark: an open source Python package for benchmarking and validating uncertainty quantification algorithms''. 
                                In: \textit{Proceedings of the 4th International Conference on Uncertainty Quantification in Computational Sciences and Engineering (UNCECOMP 2021)}, Athens, Greece. (Paper \& Talk)\\
                    & \underline{E. Fekhari}, B. Iooss, V. Chabridon, J. Muré (2022). 
                    ``Efficient techniques for fast uncertainty propagation in an offshore wind turbine multi-physics simulation tool''.
                    In: \textit{Proceedings of the 5th International Conference on Renewable Energies Offshore (RENEW 2022)}, Lisbon, Portugal. (Paper \& Talk)\\
        
                    & \underline{E. Fekhari}, V. Chabridon, J. Muré and B. Iooss (2023). 
                    ``Bernstein adaptive nonparametric conditional sampling: a new method for rare event probability estimation''\footnote{Rewarded by the ``CERRA Student Recognition Award'' (\url{https://icasp14.com/presenter/awards/})}.
                    In: \textit{Proceedings of the 13th International Conference on Applications of Statistics and Probability in Civil Engineering (ICASP 14)}, Dublin, Ireland. (Paper \& Talk)\\
        
                    & A. Lovera, \underline{E. Fekhari}, B. Jézéquel, M. Dupoiron, M. Guiton and E. Ardillon (2023). 
                    ``Quantifying and clustering the wake-induced perturbations within a wind farm for load analysis''. 
                    In: \textit{Journal of Physics: Conference Series (WAKE 2023)}, Visby, Sweden. (Paper)\\
                    
                    & E. Vanem, \O{}. Lande, \underline{E. Fekhari} (2024). 
                    ``A joint probability distribution model for multivariate wind and wave conditions''.
                    In: \textit{Proceedings of the ASME 2024 43th International Conference on Ocean, Offshore and Arctic Engineering (OMAE 2024)}, Singapore. (Paper to appear)\\
        \hline
\shortstack{Int. Conf.\\Short Abs.}  & \underline{E. Fekhari}, B. Iooss, V. Chabridon, J. Muré (2022).
                    ``Numerical Studies of Bayesian Quadrature Applied to Offshore Wind Turbine Load Estimation''.
                    In: \textit{SIAM Conference on Uncertainty Quantification (SIAM UQ22)}, Atlanta, USA. (Talk)\\
        
                    & \underline{E. Fekhari}, B. Iooss, V. Chabridon, J. Muré (2022). 
                    ``Model predictivity assessment: incremental test-set selection and accuracy evaluation''.
                    In: \textit{22nd Annual Conference of the European Network for Business and Industrial Statistics (ENBIS 2022)}, Trondheim, Norway. (Talk)\\

                    & \underline{E. Fekhari}, V. Chabridon, J. Muré and B. Iooss (2024). 
                    ``Sensitivity-Informed Nonparametric Adaptive Conditional Sampling for Robust Reliability Analysis''. 
                    In: \textit{SIAM Conference on Uncertainty Quantification (SIAM UQ24)}, Trieste, Italy. (Talk)\\
        \hline
        Nat. Conf.  & \underline{E. Fekhari}, B. Iooss, V. Chabridon, J. Muré (2022).
                    ``Kernel-based quadrature applied to offshore wind turbine damage estimation''. 
                    In: \textit{Proceedings of the Mascot-Num 2022 Annual Conference (MASCOT NUM 2022)}, Clermont-Ferrand, France. (Poster)\\
        
                    & \underline{E. Fekhari}, B. Iooss, V. Chabridon, J. Muré (2023).
                    ``Rare event estimation using nonparametric Bernstein adaptive sampling''. 
                    In: \textit{Proceedings of the Mascot-Num 2023 Annual Conference (MASCOT-NUM 2023)}, Le Croisic, France. (Talk)\\
        \hline
        Invited Lec.& Le Printemps de la Recherche 2022, Nantes, France. «Traitement des incertitudes pour la gestion d’actifs éoliens». (Talk)\\

                    & Journées Scientifiques de l’Eolien 2024, Saint-Malo, France. «Evaluation probabiliste de la fiabilité en fatigue des structures éoliennes en mer». (Talk)
                    
        \end{tabularx}    
\end{center}